Hydras \& Co.

### 2022-01-14 doc/gaia-chapter.tex
fix a typo in gaia-chapter.tex
first try
utf8 omega accepted

\subsubsection{A few constants}
For each constant: $0$, $1$, \dots, $n$ and $\omega$ we prove
that the \texttt{hydras}' definition refines \texttt{gaia}'s.
\inputsnippets{T1Bridge/constantRefs}

@@

\inputsnippets{T1Bridge/gE0Def}
\inputsnippets{T1Bridge/E0EqP}

@@

\inputsnippets{T1Bridge/E0iotaPi}

>>>>

\subsubsection{A few constants}
For each constant: $0$, $1$, \dots, $n$ and ω, ω again, we prove
that the \texttt{hydras}' definition refines \texttt{gaia}'s.
\inputsnippets{T1Bridge/constantRefs}

\inputsnippets{T1Bridge/utf8try}

@@

\inputsnippets{T1Bridge/E0Def}
\inputsnippets{T1Bridge/E0EqP}

@@

\inputsnippets{T1Bridge/gE0iotaPi}
